---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# encryptedRmd

Self-encrypt html markdown reports using sodium. The goal is to provide functionality to encrypt markdown html documents and share them with others securely. The code needed to decrypt the file is bundled into the exported html file.

** EXPERIMENTAL **

## Installation

``` r
remotes::install_github("dirkschumacher/encryptedRmd")
```

## Functions

### Encrypt html files

```{r}
library(encryptedRmd)
encrypt_html_file("devel/example/test.html", output_path = "docs/test.encrypted.html")
```

You can take a look at the exported file [here](https://dirkschumacher.github.io/encryptedRmd/test.encrypted.html) and use the key printed above to decrypt it.

### Encrypted rmarkdown html format

```yml
---
title: "test"
output: encryptedRmd::encrypted_html_document
---
```

See [here](devel/example/) for an example. After knitting the document is encrypted with a random key and the file is stored in the same directory together with the key.

## Inspiration

Inspired and based on the work by @derhuerst on [self encrypting html pages](https://github.com/derhuerst/self-decrypting-html-page).
